### 2019-12-10 CV/cv-sections/papers.tex
site update

\cventry
{Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik} % Role
{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} % Title
{} % Location
{Dec. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://drive.google.com/file/d/12aISV2e5XZGDxkr_wg9ILoC27HqoYJsV/view}{NeurIPS 2019 Workshop: Beyond First Order Methods in Machine Learning}}
	\end{cvitems}
}

@@

\cventry
{Konstantin Mishchenko, Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Yura Malitsky} % Role
{Revisiting Stochastic Extragradient} % Title
{} % Location
{May 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1905.11373}{arXiv 2019}}
	\end{cvitems}
}

>>>>

\cventry
{Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik} % Role
{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} % Title
{} % Location
{Dec. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://sites.google.com/site/optneurips19/}{NeurIPS 2019 Workshop: Beyond First Order Methods in Machine Learning}}
		\item {\href{https://arxiv.org/pdf/1912.01597.pdf}{arXiv 2019}}		
	\end{cvitems}
}

@@

\cventry
{Konstantin Mishchenko, Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Yura Malitsky} % Role
{Revisiting Stochastic Extragradient} % Title
{} % Location
{May 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://sgo-workshop.github.io}{NeurIPS 2019 Workshop: Bridging Game Theory and Deep Learning}}
		\item {\href{https://arxiv.org/abs/1905.11373}{arXiv 2019}}
	\end{cvitems}
}
